The \dealii Library, Version 9.5

### 2023-05-27 9.5/paper.tex

The 9.5 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_4_2_and_9_5_0.html}
{around X incompatible changes}; see \cite{changes95}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority changes internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
  \item 
\todo[inline]{Write}
\end{itemize}

>>>>

The 9.5 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_4_2_and_9_5_0.html}
{around X incompatible changes}; see \cite{changes95}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority changes internal
interfaces that are not usually used in external
applications. That said, the following are worth mentioning since they
may have been more widely used:
\begin{itemize}
  \item
  The class \texttt{hp::DoFHandler} has been removed. The standard \texttt{DoFHandler} now implements all hp-related functionality.

  \item
  We improved the type safety for active and future FE indices in the \texttt{DoFHandler} implementation by introducing a new datatype \texttt{types::fe\textunderscore{}index}. Corresponding functions like \texttt{DoFCellAccessor::active\textunderscore{}fe\textunderscore{}index()} and \texttt{DoFHandler::get\textunderscore{}active\textunderscore{}fe\textunderscore{}indices()} have changed their interface.

  \item
  This rework also affects the serialization process of active FE indices. You will need to recreate your serialized data \textit{if and only if} you work in hp-mode. You can continue to use previously generated data if you do not use hp-mode. A special case forms \texttt{parallel::distributed::Triangulation} for non-hp data, in which it is sufficient to increase the version in the metadata file by one from ``4'' to ``5''.

  \item
  ...
\end{itemize}
\todo[inline]{Write}
